Production-maintenance scheduling in complex machinery

### 2024-03-22 Paper.tex
Minor fixes. Started adding subsection in Section 4

\keywords{Production-maintenance scheduling \and Dantzig-Wolfe decomposition \and MINLP \and Resource allocation}
\end{abstract}
%
%
%
\todo[inline]{KB: to make git diffs more meaningful, it helps to write each sentence on its own line. You don't have to change everything now, but you can change this in the parts that you edit anyway.}
\todo[inline]{KB: your use of commas is often excessive; it might come from a difference between punctuation rules in your language and English. I am removing some unneeded commas as I go, but this is something you might want to watch out for generally.}
\label{sec:intro}
\section{Introduction}

@@

  This article is organized as follows: Section~\ref{sec:intro} frames the problem and provides a light background on production-maintenance problems and on maintenance practices, besides presenting the related work. In Section~\ref{sec:model}, the compact formulation is presented. Section~\ref{sec:DW} shows the Dantzig-Wolfe reformulation of this compact model, with implementation details appearing in Section~\ref{sec:implementation}. Due to the difficulty of this model we need some heuristics and consider some simplifications in Section~\ref{sec:heuristics}. Section~\ref{sec:tests} presents the experimental setup and in Section~\ref{sec:results} the results are shown and discussed. We conclude the paper in Section~\ref{sec:conclusion}. \\

@@

Below we present a general formulation of the production-maintenance scheduling problem. The variables are represented by lowercase letters ($x,y,r$), parameters by uppercase letters with a different font (\cmss{C}, \cmss{Q}, \cmss{M}, etc.), and sets by uppercase letters with a third font ($\mathcal{N}, \mathcal{K}, \mathcal{Z}$). Varoabçes and parameters will have subscripts and superscripts. For example, $r_{n,t}^k$ is the variable $r$ for component $k$ of machine $n$ at the time period $t$, and this nomenclature is standardized across the model.

@@

\section{Extended formulation implementation}
\label{sec:implementation}

\todo[inline]{KB: you should be consistent about the capitalisation of the section titles (i.e. same level headings should have similar capitalisation).}
\todo[inline]{KB: I would add some introductory text here.}

@@

  Mathematically, the left branch adds the constraint $\sum_{\lambda \mid x_\lambda = 1} \lambda \leq \left \lfloor{k}\right \rfloor$.\todo{KB: make sure you define $x_\lambda$ somewhere}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=.5\textwidth]{Media/contraction_example.png}
    \caption{Example of the greedy solution not being optimal}
    \label{fig:bad_greedy_solution}
\end{figure}
\todo[inline]{KB: I would expand the caption to briefly explain what in the figure stands for what.}

@@

\iffalse
\subsubsection{1M}

This heuristic takes the same initial observation of the PF heuristic, that the production has a disproportionate impact in the model, and assigns a production vector to each machine proportional to the number of machines. This heuristic can be thought of as the previous heuristic with a production vector of $1/|\mathcal{N}|$, but still with freedom on the remaining variables, even if they are heavily constrained. It works best when the machines are similar. If that is not the case, the production can be fixed to values proportional to the effectiveness of the machines, according to some heuristic decision.

The model is optimized for a single machine with the production vector assigned to it, and its solution is then copied to the remaining ones.

If we have only one type of machine, diving the demand by the number of machines can give us a near-optimal solution. However, this is not necessarily true, as the following example shows.

\begin{example}
    For simplicity, assume that we are studying machines with a single component, component $A$, and that there are $n$ identical machines to be maintained. Choosing appropriate parameters, suppose that by dividing the demand by $n$, the number of machines, and assigning that demand to one machine, component $A$ does not require maintenance if the number of considered periods is less than \cmss{T}, but requires one maintenance action when they equal \cmss{T}. Then, assigning maintenance to $A$ at time period $\cmss{T}-1$ would give us an optimal solution, one obtainable by the heuristic. Copying this solution to the remaining machines means that the fleet ends the study with very healthy components. Again, by choosing appropriate parameters, the demand of the final time period may be satisfiable by a proper subset of the fleet. This means that the complement of this subset incurred unnecessary maintenance, and thus the heuristic did not produce an optimal solution. 
\label{ex:sub_optimal_1M}
\end{example}
\fi

@@

\section{Benchmark Instances Used}
\label{sec:tests}
\todo[inline]{KB: no need for a separate section to describe the instances. You can make one section for the computational experiments and include this as a subsection.}

@@

For every instance, we ran three formulations: the compact formulation, the extended formulation with exact pricing, and the extended formulation with heuristic pricing.\todo{KB: specify how these formulations are denoted in the tables}

@@

\section{Results and Analysis}\label{sec:results}

>>>>

\keywords{Production-maintenance scheduling \and Dantzig-Wolfe decomposition \and MINLP \and Resource allocation}
\end{abstract}
%
%
%
\todo[inline]{KB: to make git diffs more meaningful, it helps to write each sentence on its own line. You don't have to change everything now, but you can change this in the parts that you edit anyway. JD@KB:Done.}
\todo[inline]{KB: your use of commas is often excessive; it might come from a difference between punctuation rules in your language and English. I am removing some unneeded commas as I go, but this is something you might want to watch out for generally.}
\label{sec:intro}
\section{Introduction}

@@

  This article is organized as follows: Section~\ref{sec:intro} frames the problem and provides a light background on production-maintenance problems and on maintenance practices, besides presenting the related work.
   In Section~\ref{sec:model}, the compact formulation is presented.
    Section~\ref{sec:DW} shows the Dantzig-Wolfe reformulation of this compact model, with implementation details appearing in Section~\ref{sec:implementation}.
    Due to the difficulty of this model we need some heuristics and consider some simplifications in Section~\ref{sec:heuristics}. 
    Section~\ref{sec:tests} presents the experimental setup, along with the results and corresponding discussion. 
    We conclude the paper in Section~\ref{sec:conclusion}. \\

@@

Below we present a general formulation of the production-maintenance scheduling problem. 
The variables are represented by lowercase letters ($x,y,r$), parameters by uppercase letters with a different font (\cmss{C}, \cmss{Q}, \cmss{M}, etc.), and sets by uppercase letters with a third font ($\mathcal{N}, \mathcal{K}, \mathcal{Z}$). 
Variables and parameters will have subscripts and superscripts. 
For example, $r_{n,t}^k$ is the variable $r$ for component $k$ of machine $n$ at the time period $t$, and this nomenclature is standardized across the model.

@@

\section{Extended Formulation Implementation}
\label{sec:implementation}

\todo[inline]{KB: you should be consistent about the capitalisation of the section titles (i.e. same level headings should have similar capitalisation). JD@KB:Done.}
\todo[inline]{KB: I would add some introductory text here.}

@@

  Mathematically, the left branch adds the constraint $\sum_{\lambda \mid x_\lambda = 1} \lambda \leq \left \lfloor{k}\right \rfloor$, where $x_\lambda$ represents the value of a specific maintenance variable $x$ in the pattern associated to master variable $\lambda$.\todo{KB: make sure you define $x_\lambda$ somewhere. JD@KB: Done.}

\subsubsection{Dual bound} ?????? WORK IN PROGRESS ?????
The following is a dual bound for the master problem: ??? WHAT IS THE NAME? NEED REFERENCE ???
$$z^\ast_{\text{RMP}} + \sum_{n \in \mathcal{N}}|\mathcal{N}_n\cdot min(0,z^\ast_{\text{PP}_n})| \leq z^\ast_{\text{MP}}$$

As one of the approaches will not always solve the pricing problems to optimality, the optimal objective value of the pricing problem can
be replaced by its dual bound, whenever available.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=.5\textwidth]{Media/contraction_example.png}
    \caption{The anticipation of the \cmss{B}-\cmss{A} maintenance in the top solution leads to the bottom solution. 
    If feasible, the bottom solution is strictly better.}
    \label{fig:bad_greedy_solution}
\end{figure}
\todo[inline]{KB: I would expand the caption to briefly explain what in the figure stands for what. JD@KB:Done.}

@@

% \iffalse
% \subsubsection{1M}

% This heuristic takes the same initial observation of the PF heuristic, that the production has a disproportionate impact in the model, and assigns a production vector to each machine proportional to the number of machines. This heuristic can be thought of as the previous heuristic with a production vector of $1/|\mathcal{N}|$, but still with freedom on the remaining variables, even if they are heavily constrained. It works best when the machines are similar. If that is not the case, the production can be fixed to values proportional to the effectiveness of the machines, according to some heuristic decision.

% The model is optimized for a single machine with the production vector assigned to it, and its solution is then copied to the remaining ones.

% If we have only one type of machine, diving the demand by the number of machines can give us a near-optimal solution. However, this is not necessarily true, as the following example shows.

% \begin{example}
%     For simplicity, assume that we are studying machines with a single component, component $A$, and that there are $n$ identical machines to be maintained. Choosing appropriate parameters, suppose that by dividing the demand by $n$, the number of machines, and assigning that demand to one machine, component $A$ does not require maintenance if the number of considered periods is less than \cmss{T}, but requires one maintenance action when they equal \cmss{T}. Then, assigning maintenance to $A$ at time period $\cmss{T}-1$ would give us an optimal solution, one obtainable by the heuristic. Copying this solution to the remaining machines means that the fleet ends the study with very healthy components. Again, by choosing appropriate parameters, the demand of the final time period may be satisfiable by a proper subset of the fleet. This means that the complement of this subset incurred unnecessary maintenance, and thus the heuristic did not produce an optimal solution. 
% \label{ex:sub_optimal_1M}
% \end{example}
% \fi

@@

\section{Computational Experiments}
\label{sec:tests}

\subsection{Benchmark instances used}
\todo[inline]{KB: no need for a separate section to describe the instances. You can make one section for the computational experiments and include this as a subsection. JD@KB:Done.}

@@

For every instance, we ran three formulations: the compact formulation, the extended formulation with exact pricing, and the extended formulation with heuristic pricing. 
In the result subsection represented by ``Compact'', ``DW'', and ``DW+PF'' respectively.\todo{KB: specify how these formulations are denoted in the tables. JD@KB: Done.}

@@

\subsection{Results and Analysis}\label{sec:results}
